\chapter{Optics}
\thispagestyle{fancy}

Optics is the branch of physics that focuses on the behavior and properties of light. It encompasses the study of how light interacts with various materials, how it propagates through space, and how it is perceived by our eyes. Optics plays a crucial role in understanding both the fundamental nature of light and its practical applications in fields such as astronomy, microscopy, telecommunications, and more. The exploration of optics has led to groundbreaking discoveries and technologies that have transformed the way we observe, communicate, and interact with the world around us. Key concepts in optics include the following:

\begin{itemize}
    \item \keyword{Reflection}: Reflection occurs when light rays bounce off a surface. The angle of incidence (the angle at which light hits the surface) is equal to the angle of reflection (the angle at which light bounces off).
    \item \keyword{Refraction}: Refraction is the bending of light as it passes from one medium to another with a different optical density. This phenomenon is responsible for the way lenses focus light and how prisms disperse it into a spectrum of colors.
    \item \keyword{Dispersion}: Dispersion is the separation of white light into its component colors (spectrum) due to the varying speeds of different colors of light through a material. This is commonly observed in rainbows and in the phenomenon of chromatic aberration in lenses.
    \item \keyword{Diffraction}: Diffraction is the bending of light waves around obstacles and the spreading of light as it passes through small openings. This phenomenon is responsible for the characteristic patterns of light and dark bands observed when light encounters obstacles or slits.
    \item \keyword{Polarization}: Polarization refers to the orientation of light waves in a particular direction. Polarized light waves vibrate in a specific plane, and the study of polarization has applications in reducing glare, 3D movie technology, and various optical instruments.
    \item \keyword{Interference}: Interference occurs when two or more light waves combine and either reinforce (constructive interference) or cancel out (destructive interference) each other. This phenomenon is exploited in applications such as thin film coatings and optical coatings on lenses.
    \item \keyword{Optical Instruments}: Optics has given rise to a wide range of instruments that manipulate and utilize light. These include lenses, mirrors, telescopes, microscopes, cameras, projectors, lasers, and fiber-optic communication systems.
    \item \keyword{Wave-Particle Duality}: One of the intriguing aspects of optics is the wave-particle duality of light. Light can exhibit both wave-like and particle-like behaviors, depending on the context of observation. This duality is a fundamental concept in quantum physics.
    \item \keyword{Holography}: Holography is a technique that captures and reconstructs the complete three-dimensional information of an object using light interference patterns. It has applications in security, art, and data storage.
    \item \keyword{Optical Phenomena}: Optics is responsible for a multitude of natural and man-made phenomena, such as mirages, rainbows, the blue color of the sky, and the functioning of the human eye.
\end{itemize}







\section{Snell's Law}

\begin{figure}
\centering

\usetikzlibrary{decorations.markings}
\tikzstyle arrowstyle=[scale=1]
\tikzstyle directed=[postaction={decorate,decoration={markings,
    mark=at position .65 with {\arrow[arrowstyle]{stealth}}}}]
\tikzstyle reverse directed=[postaction={decorate,decoration={markings,
    mark=at position .65 with {\arrowreversed[arrowstyle]{stealth};}}}]
\begin{tikzpicture}

    % define coordinates
    \coordinate (O) at (0,0) ;
    \coordinate (A) at (0,3) ;
    \coordinate (B) at (0,-3) ;
    
    % media
    \fill[red!25!,opacity=.3] (-4,0) rectangle (4,3);
    \fill[blue!25!,opacity=.3] (-4,0) rectangle (4,-3);
    \node[right] at (2,1.5) {Medium 1};
    \node[left] at (-2,-1.5) {Medium 2};

    % axis
    \draw[dash pattern=on5pt off3pt] (A) -- (B) ;

    % rays
    \draw[red,ultra thick,reverse directed] (O) -- (130:3.92);
    \draw[blue,directed,ultra thick] (O) -- (-70:3.2);

    % angles
    \draw (0,1) arc (90:130:1);
    \draw (0,-1.4) arc (270:290:1.4) ;
    \node[] at (280:1.8)  {$\theta_{2}$};
    \node[] at (110:1.4)  {$\theta_{1}$};
\end{tikzpicture}
\caption{\footnotesize Light traveling through two mediums. The upper left position of the red vector (in medium 1)is $(0,A)$ and the lower right position of the blue vector (in medium 2) is $(B,0)$.}
\label{fig:snells_law}
\end{figure}

Consider two mediums, where light travels through them at some angle starting and point $(0, A)$ and ending at point $(B, 0)$ (see Fig. \ref{fig:snells_law}). The first medium will be denoted with subscript $1$, and the second with subscript $2$. Therefore, the light traveling through a medium $i$ has velocity $v_i$, a distance $d_i$ that the lgiht travels, an angle relative to a vertical line at the intersection of mediums as $\theta_i$, a refractive index of $n_i = \frac{c}{v_i}$. The distance $d_i$ has horizontal and vertical components of $x_i$ and $y_i$ respectively, which gives a total distance of $d_i = \sqrt{x_i^2+y_i^2}$ per the \keyword{Pythagorean Theorem}. The time it takes for light to travel through each medium is $t_i$, and applying the distance formula gives $v_i = \frac{d_i}{t_i} \implies t_i = \frac{d_i}{v_i}$. The total time taken for the light to travel from point $(0, A)$ to $(B, 0)$ is thus 

\begin{align}
t=t_1+t_2 = \frac{d_1}{v_1} + \frac{d_2}{v_2} = \frac{\sqrt{x_1^2+y_1^2}}{v_1} + \frac{\sqrt{x_2^2+y_2^2}}{v_2} \label{snells_law_derivation_1}
\end{align}

Given some path from $(0, A)$ to $(B, 0)$, the velocities, the vertical distances, and $B$ are constant. Therefore, we can write $x_2$ in terms of $B$ as $x_2 = B - x_1$, which allows us to write \ref{snells_law_derivation_1} in terms of $x_1$ and constants. Thsi gives

\begin{align}
t = \frac{\sqrt{x_1^2+y_1^2}}{v_1} + \frac{\sqrt{(B - x_1)^2+y_2^2}}{v_2} \label{snells_law_derivation_2}
\end{align}

Since $x_1$ is the only non-constant value, we can take the derivative set to zero, $\frac{dt}{dx_1}=0$, to calculate a minimum value of time with respect to $x_1$. Taking the derivative of \ref{snells_law_derivation_2} gives

\begin{align}
\frac{dt}{dx_1} = \frac{2x_1(x_1^2+y_1^2)^{-1/2}}{v_1} - \frac{2(B - x_1)((B - x_1)^2+y_2^2)^{-1/2}}{v_2} = \frac{2x_1}{v_1\sqrt{x_1^2+y_1^2}} - \frac{2x_2}{v_2\sqrt{x_2^2+y_2^2}} \label{snells_law_derivation_3}
\end{align}

Each distance can be written in terms of the angle that the light makes with the vertical line by applying simple trigonometry which gives $\sin(\theta_i)=\frac{x_i}{d_i}=\frac{x_i}{\sqrt{x_i^2+y_i^2}}$. This allows \ref{snells_law_derivation_3} to be written as

\begin{align}
\frac{dt}{dx_1} = \frac{2}{v_1}\sin(\theta_1) - \frac{2}{v_2}\sin(\theta_2) \label{snells_law_derivation_4}
\end{align}

Setting \ref{snells_law_derivation_4} to zero to satisfy $\frac{dt}{dx_1}=0$ gives

\begin{align}
0 = \frac{2}{v_1}\sin(\theta_1) - \frac{2}{v_2}\sin(\theta_2) \implies v_1\sin(\theta_2) = v_2\sin(\theta_1) \label{snells_law_derivation_5}.
\end{align}

The refractive index is defined by $n_i = \frac{c}{v_i}$. Plugging this into \ref{snells_law_derivation_5} and rearranging gives Snell's Law as it is typically written. \keyword{Snell's Law}, also known as the \keyword{Law Of Refraction}. is a physical formula that describes how light of other waves change direction when passing through different mediums. This law works because the light takes the path for which the travel time from one medium to another is minimized (in time). Solving this problem gives \keyword{Snell's Law}. This law follows from \keyword{Fermat's principal of least time}.

\begin{fancybox}[Snell's Law (The Law Of Refraction) \label{Snell's Law}]{1}
    Given two mediums, light traveling from medium 1 to medium 2 will refract at an angle given by the following relationship:
    \begin{align}
        \frac{\sin(\theta_1)}{\sin(\theta_2)} = n = \frac{n_2}{n_1} = \frac{v_1}{v_2} \label{Snell's Law Eqn}
    \end{align}
    where $n_1$ and $n_2$ are the refractive indices and $v_1$ and $v_2$ are the phase velocities in the two media.
\end{fancybox}


