\chapter{Relativity}
\thispagestyle{fancy}

Relativity refers to two groundbreaking theories developed by Albert Einstein: \keyword{Special Relativity} and \keyword{General Relativity}. Both theories revolutionized our understanding of the universe and how it functions, especially at high speeds and in the presence of strong gravitational fields.

\begin{itemize}
	\item \keyword{Special Relativity}: Introduced in 1905, Special Relativity deals with the behavior of objects moving at constant velocities, especially near the speed of light. It is based on two postulates: the principle of relativity (laws of physics are the same for all inertial observers) and the constancy of the speed of light in a vacuum. Key principles of Special Relativity include:
	\begin{itemize}
		\item \keyword{Time Dilation}: Moving clocks appear to run slower compared to stationary clocks from the perspective of an observer at rest.
		\item \keyword{Length Contraction}: Moving objects appear shorter in the direction of motion relative to a stationary observer.
		\item \keyword{Mass-Energy Equivalence}: $E_0=m_0c^2$, where $E_0$ is the rest energy, $m_0$ is the rest mass, and $c$ is the speed of light. This famous equation shows that mass and energy are interchangeable.
	\end{itemize}

	\item \keyword{General Relativity}: Formulated in 1915, General Relativity is a theory of gravity that describes the curvature of spacetime caused by the presence of mass and energy. Unlike Newtonian gravity, which considers gravity as an attractive force between masses, General Relativity attributes gravity to the curvature of spacetime caused by massive objects. Key principles of General Relativity include:
	\begin{itemize}
		\item \keyword{Curved Spacetime}: Massive objects like stars and planets curve the fabric of spacetime around them, and other objects move along the curved paths in response to this curvature.
		\item \keyword{Gravitational Time Dilation}: Clocks in stronger gravitational fields (e.g., near massive objects) run slower compared to clocks in weaker fields.
		\item \keyword{Gravitational Waves}: General Relativity predicts the existence of gravitational waves, ripples in spacetime caused by violent cosmic events.
	\end{itemize}
\end{itemize}

Both Special and General Relativity have been confirmed through numerous experiments and observations, and they have far-reaching implications for our understanding of the cosmos. Special Relativity's effects become significant at high speeds, near the speed of light, while General Relativity is essential for describing gravity and the behavior of massive objects, such as stars, galaxies, and black holes. These theories have not only revolutionized fundamental physics but have also influenced technology, astronomy, and our perception of the nature of space, time, and the universe.


\section{Time}

What is time? This is a big question and there are many different levels of definitions that can be given in varying contexts. One definition, given by the Oxford Languages Dictionary follows

\begin{quotationbox}
``The indefinite continued progress of existence and events in the past, present, and future regarded as a whole.''
\end{quotationbox}

This definition is not very useful in quantifying time in a useful manner. \keyword{Time} is a fundamental concept in physics and philosophy that represents the sequence of events, changes, or movements in the universe. It is an abstract dimension in which events appear to occur in a chronological order, including the past, present, and future. Time appears as a continuous and one-directional flow, and it is often measured and quantified in relation to periodic or repetitive phenomena, such as the rotation of celestial bodies or the oscillations of certain particles. In modern physics, time is intricately connected to the fabric of spacetime, and its nature is further explored in theories like the theory of relativity and quantum mechanics. One can think of time in reference to something with regular periodicity, such as the rotation of the earth. We can just say that we base our definition of time on the repetition of some apparently periodic event. Of course many questions can follow.

\begin{questions}
	\item How do we regard time as existing in the past or future (or even the now)?
 	\item How is time different for different observers?
  	\item Does everyone perceive time similarly?
   	\item Can we measure time accurately without relying on periodic events like the rotation of the earth?
    	\item Is time an objective reality or a human construct?
     	\item How does time interact with other fundamental aspects of the universe, such as space and matter?
      	\item Are there alternative ways to conceptualize time that differ from our current understanding?
       	\item Is time one-directional and can be be stopped, slowed down, or reversed?
\end{questions}

For measurements of time, typically a periodic event is used and counted, such as a watch running at a stable \keyword{frequency}\footnote{note that a frequency is not easily definable without the concept of time.} For most day-to day events, this is simple and easy to do and we can get smaller units of time by dividing our periodic events into smaller equal units of time. For very long periods of time, atomic half-lives can be used to deduce time intervals, such as the age of objects. This typically relies on assumptions and assuming that the known methods and laws are the same in the past as they are now. For very small or consistent units of time, electronic oscillators or atomic clocks can be used. And example of an atomic clock is a cesium atomic. A \keyword{cesium atomic clock} is a highly accurate and precise timekeeping device that operates based on the resonant frequency of cesium atoms. It uses the transition between two energy levels in cesium atoms to generate a stable and constant microwave signal. By counting the number of microwave oscillations, cesium atomic clocks can measure time with incredible accuracy, making them essential tools for applications in scientific research, navigation, and communication systems.

\begin{questions}
	\item Is there a smallest unit of possible time?
\end{questions}


\section{Distances}

\keyword{Distance} refers to the numerical measurement of the physical separation between two points or objects in space. It is a fundamental concept in physics and is typically expressed in units such as meters, kilometers, feet, or miles. Distance is a scalar quantity, meaning it only has magnitude and no direction, and it plays a crucial role in various scientific and everyday contexts, including navigation, transportation, and spatial analysis. From a mathematical sense, distance can typically be defined and/or determined exactly. In reality, this is not the case. There are generally errors associated with measured, deduced, or calculated distances for physical matter.  

\begin{questions}
	\item Are distances an absolute measurement?
\end{questions}

\keyword{Triangulation} is a geometric method used to determine the distance or position of a point by forming triangles with known sides or angles. In the context of surveying and navigation, triangulation involves measuring the angles from two known points to an unknown point and using trigonometric principles to calculate its distance or location. This technique is widely employed in various fields, such as cartography, geodesy, astronomy, and GPS (Global Positioning System) to accurately determine positions and distances on the Earth's surface or in three-dimensional space. Triangulation is commonly used to determind the distance that planets, meteors, satellites, stars and other objects are from an observer. Other methods of determining distances include using electromagnetic radiation and calculating the time associated with its travel to deduce distances. there are many unique methods for deducing both large and small distances.

Very small objects cannot be seen (objects that are smaller than the wavelength of visibuel light (about $5 \times 10^{-7}$ meters). \keyword{Electron microscopes} can be used to `photograph' objects down to about $10^{-8}$ meters. At even smaller scales, x-rays can be used to determine/deduce even smaller scales as low as $10^{-10}$ meters by looking at the pattern of scattering off of atoms in a crystal. At the atomic nucleus scale, we can deduce sizes by sending high energy particles through materials and calculating how many do not make it through - deducing a cross section of a nucleus. The radius of a nucleus can be determined by

\begin{align}
 \pi r^2 = \sigma = \frac{A}{N}\frac{n_1-n_2}{n_1},
\end{align}

where $A$ is the area of a slab of material containing $N$ atoms, $\sigma$ is the cross-sectional area of the nucleus, $n_1$ is the number of particles sent into the material with a beam and $n_2$ is the number that passed out the other side. Using this equation in conjunction with experiments, the nuclei of atoms are found to be on the scale of $10^{-15}$ meters, which is called the \keyword{fermi}, in honor of Enrico Fermi (1901–1954).





%\input{./chapters/relativity/special_relativity}






