\begin{center}
	\textbf{Preface}
\end{center}

This document is a compilation of ideas, scratch work, derivations, useful formulas, definitions, constants, and general information used for my own studies as a reference while furthering self education. These are my notes. It's purpose is to provide a complete 'compendium' per say of various ideas used often. All the material in this document was either directly copied from one of the references listed at the end or derived from scratch. On occasion \textit{typos may exist} due to human error but will be corrected when discovered.
	
The version number is updated every time the document is distributed, printed for distribution, or a major update is added. This ensures that there is no two copies with different information and similar version numbers. The latest update date is automatically set to the current date each time the document is edited. Please refrain from distributing this handbook without permission from the original author/compiler. This book is formatted for printing.

\begin{center}
	\textbf{Topics Covered In This Book}
\end{center}

\begin{multicols}{2}
\begin{itemize}
	\item Machine Learning
	\item Artificial Intelligence
	\item Modeling
	\item Psychology
\end{itemize} 
\end{multicols}

The information in this book is in no way limited to the topics listed above. They serve as a simple guideline to what you will find within this document. For more information about this book or details about how to obtain your own copy please visit:
\begin{center}
	https://torodean.github.io/
\end{center}

\begin{quotation}
``Scientific theories deal with concepts, not with reality. All theoretical results are derived from certain axioms by deductive logic. In physical sciences the theories are so formulated as to correspond in some useful sense to the real world, whatever that may mean. However, this correspondence is approximate, and the physical justification of all theoretical conclusions is based on some form of inductive reasoning.'' - Athanasios Papoulis (Probability, Random Variables, and Stochastic Processes book)
\end{quotation}

\begin{center}
	\textbf{Disclaimer}
\end{center}

This book contains formulas, definitions, and theorems that by nature are very precise. Due to this, some of the material in this book was taken directly from other sources such as but not limited to Wolfram Mathworld. This is only such in cases where a change in wording could cause ambiguities or loss of information quality.  Following this, all sources used are listed in the references section and cited when used.
